\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% serif
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{2.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{flushright}
  \color{gray}
  \item
\end{flushright}

\vspace{-8pt}

\begin{center}
    \textbf{\Huge \scshape Dhruv Puri} \\ \vspace{8pt}
    \small 
    \faIcon{briefcase}
    \href{https://dhruvpuri.xyz/}
    {\underline{dhruvpuri.xyz}}
    \faIcon{github}
    \href{https://github.com/slashexx}{\underline{github.com/slashexx}} $  $
    \faIcon{linkedin}
    \href{https://linkedin.com/in/dhruvpuri-slashex}{\underline{linkedin.com/in/dhruvpuri-slashex}} $  $
    \faIcon{envelope}
    \href{mailto:dhruvpuri.35@gmail.com}
    {\underline{dhruvpuri.35@gmail.com}}
    
\end{center}

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Dayananda Sagar College of Engineering}{Sept. 2027}
      {B.E. Information Science}{CGPA: 9.58}
  \resumeSubHeadingListEnd
% -------------------- SKILLS --------------------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{Languages}{: Java, Go, Typescript, Python} \\
     \textbf{Frameworks and Libraries}{: Node.js, Express, Next.js} \\
     
     \textbf{Tools}{: Linux, Git, GitHub Actions, Firebase, Docker, Kubernetes, GitOps}     
     
    }}
 \end{itemize}
 \vspace{-16pt}
 
% -------------------- EXPERIENCE --------------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://wecofy.com/}{WeCofy}}{December 2024 - Present}
  {Full-Stack Developer : Next.js, Node.js, Express, MongoDB}{Intern : Remote}
  \resumeItemListStart
  \resumeItem{Worked on \textbf{Juristo}, an \textbf{AI-powered platform} providing \textbf{legal guidance} to the general public.}
  \resumeItem{Designed and implemented a scalable \textbf{developer API service} enabling third-party integration with \textbf{Juristo’s AI features}, tailored to various subscription tiers.}
  \resumeItem{Integrated advanced \textbf{rate-limiting mechanisms}, ensuring optimized usage for different subscription models while maintaining system \textbf{performance} and \textbf{reliability}.}
  \resumeItemListEnd






\resumeSubHeadingListEnd

\vspace{-16pt}

% -------------------- PROJECTS --------------------
\section{Projects}
    \resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{CodeBrewery} $|$ \footnotesize\emph{Golang, Docker, Kubernetes, GitHub Actions, TypeScript}}{\faIcon{github}\href{https://github.com/slashexx/CodeBrewery}{\underline{CodeBrewery}}}

\resumeItemListStart
    \resumeItem{Developed a cutting-edge online IDE allowing users to \textbf{write, compile, and run} code across multiple languages, leveraging a \textbf{microservices architecture} with \textbf{Go} for the backend.}
    \resumeItem{Employed \textbf{Docker} for \textbf{containerization} and \textbf{Kubernetes} for orchestration, ensuring seamless deployment and scalability.}
    \resumeItem{Set up \textbf{CI/CD} pipelines with \textbf{GitHub Actions} and \textbf{YAML} to automate testing and deployment, improving development efficiency.}
    \resumeItem{Implemented thorough testing for backend services in \textbf{Go} and frontend components in \textbf{Jest} to maintain code quality.}
    \resumeItem{Configured \textbf{Docker Compose} for local development, streamlining project setup. \href{https://codebrewery.vercel.app}{\textcolor{blue}{[Link]}}}
\resumeItemListEnd


\vspace{-4pt}


\resumeProjectHeading
{\textbf{KisanSetu} $|$ \footnotesize\emph{Node.js, Express, WebSocket, Solidity, Docker, Firebase}}{\faIcon{github}\href{https://github.com/slashexx/kisansetu}{\underline{Kisansetu}}}

\resumeItemListStart
    \resumeItem{Developed a blockchain platform for secure contract farming agreements between farmers and buyers.}
    \resumeItem{Integrated \textbf{smart contracts} in \textbf{Solidity} for transparent and reliable transactions.}
    \resumeItem{Implemented features like \textbf{real-time price negotiation}, \textbf{direct communication}, and \textbf{automated payments}.}
    \resumeItem{Deployed the application with \textbf{Docker} and used \textbf{Firebase} for authentication and data management. \href{kisansetu.onrender.com}{\textcolor{blue}{[Link]}}}
\resumeItemListEnd

    \resumeSubHeadingListEnd
\vspace{-14.5pt}

 % ------------------Open source----------
\section{Open Source Contributions}  
\resumeSubHeadingListStart  

\resumeProjectHeading  
{\textbf{Prometheus Operator (CNCF)} $|$ \footnotesize\emph{Golang, GitHub Actions, CI/CD, actionlint}}{Nov. 2024}  
\resumeItemListStart  
\resumeItem{Refactored the \textbf{OVHCloudSDConfig} validation logic as part of the ongoing ScrapeConfig API refactor, ensuring compliance with Prometheus version requirements and improving test coverage for unsupported field handling. \href{https://github.com/prometheus-operator/prometheus-operator/pull/7238}{{[\underline{PR}]}}}  
\resumeItem{Enhanced CI/CD reliability by implementing a \textbf{GitHub Actions workflow linter} using \textbf{actionlint}, ensuring accurate and consistent YAML configurations.\href{https://github.com/prometheus-operator/prometheus-operator/pull/7123}{{[\underline{PR}]}}}  
\resumeItemListEnd  

\resumeProjectHeading  
{\textbf{KCL Programming Language (CNCF)} $|$ \footnotesize\emph{Rust, Crypto}}{Oct. 2024}  
\resumeItemListStart  
\resumeItem{Added support for \textbf{filesha512} and \textbf{fileblake3} hashing functions by contributing to the crypto module of the KCL programming language, significantly enhancing its \textbf{cryptographic capabilities}.}  
\resumeItem{Implemented efficient file hashing operations with robust error handling, improving reliability and performance across diverse file types. \href{https://github.com/kcl-lang/kcl/pull/1697}{{[\underline{PR}]}}}  
\resumeItemListEnd  


\resumeSubHeadingListEnd

\vspace{-11pt}  

% -------------------- EXTRA-CURRICULAR --------------------
\section{Extracurricular} \vspace{0.5pt}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0.08em, topsep=1pt]
    \item \textbf{Winner, Grand prize:} at Hackverse, held at NITK.
    % \item \textbf{Winner:} at Clone Wars.
    \item \textbf{2nd Runner Up:} Capture the Flag Competition hosted by Point Blank 
    \item \textbf{2nd Runner Up:} HackSprint, part of Ignite 2.0
    \item \textbf{2* at Codechef:} Rating: 1414
\end{itemize}

\end{document}